A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
algorithms used slide
move things around a bit

\section{Algorithms Used}

\subsection{Decision Trees}
\frame
{
}

@@

\subsection{Inductive Logic Programming}
\frame
{
}

\subsection{Bayesian Classifiers}
\frame
{
}

\section{Conducted Experiments}
\frame
{
}

>>>>

\section{Algorithms Used}
\frame
{
  \frametitle{Algorithms Used}

  \begin{itemize}
    \item<1-> Decision trees

    \begin{itemize}
      \item<1-> ID3
      \item<1-> C4.5
      \item<1-> CART
      \item<1-> Random Forest
      \item<1-> Alternating Decision Trees (ADTree)
    \end{itemize}

    \item<1-> Rule Induction

    \begin{itemize}
      \item <1-> CN2
    \end{itemize}

    \item<1-> Inductive Logic Programming: using Aleph

    \item<1-> Bayesian Networks. Using different search algorithms:

    \begin{itemize}
      \item<1-> Genetic Search
      \item<1-> Hill Climbing
      \item<1-> Simulated Annealing
    \end{itemize}

  \end{itemize}
}

\section{Conducted Experiments}
\frame
{
  \frametitle{Conducted Experiments}

  \begin{itemize}
    \item<1-> Classifiers were built using the train set and then tested against the test set
    \item<1-> C4.5, Random Forest, CART, ADTree and Bayesian classifiers built using Weka
    \begin{itemize}
      \item<1-> Various parameters available in Weka algorithms were experimented in hope of getting better error rates
      \item<1-> Every missing value was replaced with modes and means
      \item<1-> Two different classifiers were trained for each algorithm, one using only discretized attributes
                and unchanged attributes to analyze how the algorithms behaves when using numeric attributes
    \end{itemize}

  \end{itemize}
}

\frame
{
  \frametitle{Conducted Experiments}
  % colocar ILP CN2 ID3!
}

@@
